$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-05-26 qdpm_paper.tex
more figure stuff

\usepackage{color}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{setspace}
\usepackage{epstopdf}
%\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

\newcommand*{\hprs}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/hrzprestar} }
}
\newcommand*{\hspr}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/hrzstarpair} }
}

@@

\newcommand*{\bhrzmv}{%
    ]{Symbols/blank_hrzmv} }
\newcommand*{\bdiag}{%
    ]{Symbols/blank_diag} }
\newcommand*{\bstr}{%
    ]{Symbols/blank_str} }

@@

\newcommand*{\threedownplqt}{%
    ]{Symbols/threedownplqt.pdf} }
\newcommand*{\threeupplqt}{%
    ]{Symbols/threeupplqt.pdf} }
\newcommand*{\threerightplqt}{%
    ]{Symbols/threerightplqt.pdf} }

@@

\newcommand*{\onedownplqt}{%
    ]{Symbols/onedownplqt.pdf} }
\newcommand*{\oneupplqt}{%
    ]{Symbols/oneupplqt.pdf} }
\newcommand*{\onerightplqt}{%
    ]{Symbols/onerightplqt.pdf} }

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c | c |}
  	\hline
    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
	\hline
    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
	\hline
    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
	\hline
    trimer & $2$ & 1 & 0 &  $\svrttrmr$ $\svrttrmrtwo$\\
	\hline
    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
	\hline
    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%
%\begin{figure}[tpb]
%\centering
%\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
%\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
%\label{fig:pentamer_moves}
%\end{figure}
%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | }
  	\hline
    $c1$, $\bar{c}1$ & $\pentmvcreate$, $\pentmvanal$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector. The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
\begin{equation}
\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
\end{equation}
Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{1,e^{i 2\pi/3},e^{-i 2\pi/3},\}$...

Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:QDPMdefects}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | }
  	\hline
      	type & $n_v$ & $Q_v^{Z_3}$  \\
	\hline
	monomer & $0$ & -1  \\
	\hline
	dimer & $1$ & 0 \\
	\hline
	trimer & $2$ & 1 \\
	\hline
	tetramer & $3$ & -1  \\
	\hline
	pentamer & $4$ & 0 \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $Z_3$ electric charges on the A sub-lattice in the QDPM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:QDPMdefects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=0.5\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{Monomer correlations in the QDPM.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimating the Gap}
    The exponetial decay of the spacial correlations shown in the previous sections 
    implieds a gap in the spectrum though it is important to determine if the lowest lying
    excitations are vison-like
    or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 
    by investigating the dimer and
    vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
    One changlenge in this type of gap estimate is in resloving the correlation functions far enough out
    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our methods used to determine
    that this particular source of systematic error is sufficinetly comparied to the gap
    estimates for different types of excitatoins.

    %At the RK point the Hamiltonian is proportional to the matrix of transitions rates the eigen modes of wich describe the time evolution of the
    %system. Since the Hamiltonian and the rate matrix share eigenvalues the lowest energy can be
    %found by looking at the fit of the imaginary time correlations far out in imaginary time where
    %the smalles exponetial dominates.

    In this paper we only investigate the gap at high symetry points in the Brillouin zone. 
    In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
    at $L/2$ and the $Z_3$ vison gap.
    \begin{table*}[htpb]
    \setlength\tabcolsep{0.3cm}
        \centering
        %\caption{$\Delta \tau = ??$}
        \label{tab:gap_table}
        \begin{tabular}{l l l l}
            \hline\hline
                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
            \hline
            $\gamma=1.0$ $(\Delta \tau =250)$    &  &  & \\
            $8\times8$  & $3.24(5)\times10^{-2}$ &                       &                            \\
            $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
            $16\times16$& $0.66(3)\times10^{-2}$ &                       &                            \\
            $18\times18$& $0.64(2)\times10^{-2}$ &                       &                            \\
            \hline
            $\gamma=0.9$ $(\Delta \tau =500)$    &  &  & \\
            $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
            $12\times12$& $0.357(2)\times10^{-2} $&$0.256(2)\times10^{-2} $ & $0.3164(7)\times10^{-2}$    \\
            $16\times16$& $0.357(3)\times10^{-2} $&$0.363(5)\times10^{-2} $ & $0.3170(9)\times10^{-2}$    \\
            $18\times18$& $0.352(2)\times10^{-2} $&$0.419(3)\times10^{-2} $ & $0.3167(7)\times10^{-2}$    \\
            \hline
            $\gamma=0.5$    & & & \\
            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
        \end{tabular}
    \end{table*}
    This table shows that the QDPM gap is relativly constant as the system size is increased and
    that the vison gap is lower than the dimer gap. In Fig.~\ref{fig:qdm_qdpm_gap} we show the
    finite size scaling of the dimer gap for both the QDM and the QDPM.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{qdm_vs_qdpm_dmr_gap.pdf}
        \caption{Here we show the finite size scaling of the dimer gap for both the QDM and the
        QDPM.}
        \label{fig:qdm_qdpm_gap}
    \end{figure}

%    \subsection{Imaginary time vison correlations}
%    \begin{figure}[htpb]
%        \centering
%        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
%        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
%        \label{fig:name}
%    \end{figure}
%
%    \subsection{Imaginary time dimer correlations}
%    \begin{figure}[htpb]
%        \centering
%        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
%        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
%        \label{fig:}
%
%    \end{figure}

@@

\label{appendix_gap_err}

When estimating the gap by calculating correlations in imaginary time one has to be sure
that the range of imaginary time is appropriate otherwise it is not meaningful to compare the relative 
sizes of the vison and dimer gaps. In
%Fig.~\ref{fig:HERE} 
we show the finite size scaling of the different gaps. For each gap estimation we wanted to reduce
if not eliminate the systematic error due to and inadiquate range of imaginary time. This was
accived by investegating the gap as a fuction of the lower cutoff in the exponential fit of. We
extended the range of $\tau$ until the gap plataued and had little dependence on the cutoff. We show an
example of the estimate of the $Z_3$ vison gap dependence on the lower cutoff of the fit for the
$HERE\times HERE$ lattice with a fraction (HERE) of $0.9$ in 
%Fig.~\ref{fig:}
%\begin{figure}[htpb]
%    \centering
%    \includegraphics[width=0.8\linewidth]{name.ext}
%    \caption{Name}
%    \label{fig:name}
%\end{figure}

NOTE: There is also some systematic error in the discritization of time. This error falls off in the QDM
as the number of flippable plaquestts. We assume this error it is small compared to the
statistical error.

\section{Imaginary time Vison Correlations}
\label{appendix_tau_corr}

    \subsection{$Z_2$ Single and Double Visons}

        \subsubsection{Single Vison}
            First we distiguish between the single and double vison correlation fuctions. We start with the
            the described by Ivanov \cite{Ivanov2004} for rewriting the single vison correlation function in a
            convieient form to implement numericaly. 
            The correlation function between two point visons $V(\bm{x}_1,\tau_1)$, and $V(\bm{x}_2,\tau_2)$ at 
            points in space $\bm{x}_1$, $\bm{x}_2$ and in imaginary time $\tau_1$ and $\tau_2$ can be writen as
            \begin{equation}
                C_{\mathrm{single}}(\bm{x}_2-\bm{x}_1,\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) \rangle
            \end{equation}
            For the $Z_2$ vison $V(\bm{x}_i,\tau_j)^2=1$ and inserting this for $i=2$ and $j=1$ between the two vison
            operators in the above equation we get 
            \begin{equation}
                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) = \big(V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1)\big)
                \big( V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) \big),
                \label{eqn:expanded_z2_v_tau_cor}
            \end{equation}

            The first product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a 
            string operator between two points on the lattice at a given imaginary time $\tau_2$ 
            \begin{equation}
                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n},
                \label{eqn:simp_z2_vison_phase}
            \end{equation}
            $n$ being the number of dimers intersecting the path between $\bm{x}_1$ and $\bm{x}_1$. This number
            can not depend on the path so one must choose a meathod of ``gauge fixing''. This can be done
            by choosing an imutable bacround configureation which also changes the phase of the
            operator $V_{12}(\tau)$ in the same way as the dynamic dimers. 
            Including the gauge fixing Eqn.~\ref{eqn:simp_z2_vison_phase} becomes
            \begin{equation}
                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n+n_{\mathrm{backround}}}.
            \end{equation}

            The second product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a string operator 
            between two points at the location but at different imaginary time $\tau_2$. 
            In order for the full path in space and
            imaginary time to maintain its path independece it can be shown that the phase 
            changes with every plaquet flip at $\bm{x}_2$. So
            \begin{equation}
                V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) = (-1)^{n_{\mathrm{flipped}}},
            \end{equation}
            where $n_{\mathrm{flipped}}$ is the number of times the plaquette at $\bm{x}_2$ is flipped.
            Finaly Eq.~\ref{eqn:expanded_z2_v_tau_cor} can be expresed as 
            \begin{equation}
                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) =
                (-1)^{n+n_{\mathrm{backround}+n_{\mathrm{flipped}}}}.
            \end{equation}
            The gap that is being estimated by looking at the single vison correlatoin function is
            the energy gap of a single vison exciation, only physical when the system has
            boundries but measureable in any system topology.

        \subsubsection{Double Vison}
            Calculating the doublue vison imaginary time correlation funciton
            \begin{equation}
                C_{\mathrm{double}}(\bm{x}_{12},\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1)V(\bm{x}_2,\tau_1) V(\bm{x}_1,\tau_2)V(\bm{x}_2,\tau_2) \rangle
            \end{equation}
            where the first product on the RHS is the string operator acting along path between points
            $\bm{x}_1$ and $\bm{x}_1$ at imaginary time $\tau_1$ and the second product is the
            string operator along a path between the same points but at $\tau_2$.

            by looking at the double vison correlation function in imaginary time the gap of a pair
            of visons is extracted.

    \subsection{$Z_3$ Single and Double Visons}

>>>>

\usepackage{color}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

%\newcommand*{\hprs}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.2ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/hrzprestar} }
%}
%\newcommand*{\hspr}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.2ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/hrzstarpair} }
%}

@@

%\newcommand*{\bhrzmv}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.2ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/blank_hrzmv} }
%}
%\newcommand*{\bdiag}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.2ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/blank_diag} }
%}
%\newcommand*{\bstr}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.2ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/blank_str} }
%}

@@

%\newcommand*{\threedownplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/threedownplqt.pdf} }
%}
%\newcommand*{\threeupplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/threeupplqt.pdf} }
%}
%\newcommand*{\threerightplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/threerightplqt.pdf} }
%}

@@

%\newcommand*{\onedownplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/onedownplqt.pdf} }
%}
%\newcommand*{\oneupplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/oneupplqt.pdf} }
%}
%\newcommand*{\onerightplqt}{%
%  \text{% change size in subscripts or superscripts
%    \includegraphics[
%      height=1.5ex,% adjust to suit
%      valign=M,% center vertically
%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
%    ]{Symbols/onerightplqt.pdf} }
%}

@@

\newcommand*{\penmvhrzleft}{%
    ]{Symbols/pentmvhorzleft.pdf} }
\newcommand*{\penmvhrzright}{%
    ]{Symbols/pentmvhorzright.pdf} }
\newcommand*{\penmvdiagup}{%
      height=5.5ex,% adjust to suit
    ]{Symbols/pentmvdiagup.pdf} }
\newcommand*{\penmvdiagdown}{%
      height=5.5ex,% adjust to suit
    ]{Symbols/pentmvdiagdown.pdf} }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c | c | c |}
  	\hline
    %type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{Z_3}$ & \\
    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{QDPM}$ & \\
	\hline
    monomer & $0$ & -1 & -2 &  -1 & $\svrtmon$  \\
	\hline
    dimer & $1$ & 0 & -1 &   0 & $\svrtdmr$ \\
	\hline
    trimer & $2$ & 1 & 0 &   1 & $\svrttrmr$ $\svrttrmrtwo$ \\
	\hline
    tetramer & $3$ & 2 & 1 &   -1 & $\svrtquat$ \\
	\hline
    pentamer & $4$ & 3 & 2 &  0 & $\svrtpent$  \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM, QFPLM, and QDPM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%
%\begin{figure}[tpb]
%\centering
%\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
%\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
%\label{fig:pentamer_moves}
%\end{figure}
%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
    \begin{tabular}{| c | c | c | c | c | c |}
  	\hline
    $c_1$& $\bar{c}_1$ & $c_2$& $\bar{c}_2$ & $c_2$& $\bar{c}_2$ \\
	\hline
    $\pentmvcreate$& $\pentmvanal$ & $\penmvhrzleft$& $\penmvhrzright$ & $\penmvdiagup$& $\penmvdiagdown$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector. The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
\begin{equation}
\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
\end{equation}
Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{0,1,-1\}$...

Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:defects}).

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_cors.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{Monomer correlations in the QDPM.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

@@
